Thank You, Next

### 2022-10-18 Manuscript/manuscript_draft.tex

\documentclass[12pt,a4paper]{article}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{amsfonts,amssymb,amsmath,amsthm}
\usepackage{multirow}
\usepackage{multicol}
\setlength{\columnsep}{1.5cm}
\usepackage{setspace}
\usepackage{url}
\usepackage{array}
\usepackage{xfrac}
\usepackage{mwe}
\usepackage{tikz}
\usepackage{lmodern}
\usepackage{flowchart}
\usetikzlibrary{shapes,arrows,positioning,calc,fit}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{booktabs}
\usepackage{float}
\usepackage{color,soul}
%\usepackage[numbers,sort&compress]{natbib}
\usepackage{hyperref}
%\usepackage{cite}
\usepackage{biblatex}
\addbibresource{References.bib}
\newcommand{\tom}[2]{{\color{red}{#1}}\footnote{\textit{\color{red}{#2}}}}
\newcommand{\ali}[2]{{\color{pink}{#1}}\footnote{\textit{\color{pink}{#2}}}}

@@

\section*{Context/Introduction}
BASELINE OF MUTUALISMS
Mutualisms are species interactions in which all involved participants benefit. They are among the most widespread species interactions\cite{Chamberlain2014,Stachowicz2005,BoucherDouglasH.1985} with diverse and dynamic consequences. 
\ali{The benefits from these interactions are called rewards, but they require investment of resources into the interaction}{I'm honestly not sure if I need to explain this idea? Do I need to include more basic mutualism background? I have tried to shift this so that I cover a small amount and then jump into the idea of partner diversity in mutualisms instead}.

Historically, scientists focused on pairwise mutualisms\cite{Bascompote2019}, however, in recent years multi-species mutualisms have been more heavily studied. 
It has become apparent that partner diversity in mutualisms often leads to non-additive fitness benefits for the focal mutualist\cite{Afkhami2014, Palmer2010}. 
This means the benefits can be greater than, less than, or equal to the sum of the benefits observed in each of the pairwise interactions with the focal mutualist that makes up the multi-species mutualism. 
This is true for many complicated reasons, including interactions between the various partners, niche overlap, temporal resource variation, and differences in partner quality, functional benefit, and competitive ability\cite{stanton2013, Afkhami2014,Boucher1982}.
Often partners have similar resource needs, particularly if they are in the same guild, which can lead to resource competition and fighting, potentially reducing benefits, or to increased quality and frequency of benefits\cite{Bascompote2019,Stanton2003}.
For this reason, pairwise studies cannot be accurately used to predict the outcomes of multi-species mutualisms\cite{Palmer2010, Stanton2013. Chamberlain2014, Song2020} which are more common.
\ali{***** Biodiversity ecosystem function? }{After this I feel like I go straight into the mechanisms which explain the potential positive effects of diversity, but I don't specify that I am talking about those and I also don't talk about any explainations of negative effects? Maybe if I include the connection between BEF theory and mutualisms here it will make a nice bridge to the benefits of diversity?} 
Observational studies on the effects of diverse multi-species mutualism systems are necessary to help us understand the demographic effects of partner diversity in mutualisms.

The diversity of partners in a multi-species mutualism causes varied demographic effects on the population of the focal mutualist which can be explained by a number of mechanisms.
Partners can vary in many ways: in some cases, the quality varies leading to some true mutualist partners, some freeloaders, and even some parasites\{Bronstein1994, Afkhami2014,Song2020,West2007,Frederickson2013}; in other cases, the function of the partner can vary, each offering a different type of reward to the focal mutualist \{Stanton2003}.
Partner quality variations can remain consistent across years and life stages of the focal mutualist or they can shift year to year. 
When partner quality remains consistent across time, meaning one partner is always better or worse than another, the effects of partner diversity on the focal mutualist can be explained by a mechanism called sampling effect.
This is the concept that if partners vary in quality, then a more diverse sample of the partner community may be more likely to include the ``best" one\cite{Batstone2018}.
When a focal mutualist in a multi-species mutualism \ali{experiences}{not sure if this is the right word} sampling effect the fitness of that focal mutualist should be equal to the fitness of the focal mutualist if they interacted only with the ``best" partner. 
In some cases the quality of partners is not constant, rather it varies year to year due to environmental limitations, such as resource shortages and niche shifts.
The effects of partner diversity in these systems can be explained by the portfolio effect, the idea that each partner is the ``best" under a different set of conditions, which vary temporally\cite{Winfree2020,Batstone2018}. 
This mechanism works almost like a financial portfolio, when one partner has a bad year another partner has a good year, meaning the overall fitness benefits of the interactions remain relatively constant across temporal variation\cite{Batstone2018}.
Finally, partners can vary functionally, meaning each partner offers a different type of reward to the focal mutualist. 
The effects of partner functional diversity can be explained by the mechanism complementarity, the idea that each partner may account for some part of the benefits, but each has different functional pathways, which together can aid in broader benefits\cite{Winfree2020,Batstone2018}.
This variation can be both within and outside of a guild, meaning the variation can be very large, such as the difference between pollination and defense among other functions\cite{Bronstein2006}, or relatively small, such as similar rewards across different life stages\{Stanton2003}. 
Complementarity in a system is evidenced by synergistic benefits, meaning the fitness of the focal mutualist is higher than the fitness if the focal mutualist interacted with any one ``best" partner\{Batstone2018}. 
\ali{These three mechanism could explain the positive partner diversity effects on a focal mutualist in a multi-species mutualism, if these benefits exist.}{I am struggling on the transition between this paragraph and the next.}

Multi-species mutualisms are a huge group of interactions which vary considerably. 
While there are many types of mutualistic interactions, including pollination, defense, dispersal, housing, and many more\cite{Bronstein2006} in this paper we will focus on defensive ant-plant mutualisms.
These involve plants which provide extra-floral nectar and/or ``housing'' to ants which in turn defend them from herbivores\cite{Bronstein1998}. 
While these interactions have been well studied\cite{} in the literature, few have considered how diversity within ant defender guilds affect the overall benefits of mutualism for the plant partner.

This study focuses on the long lived \textit{Cylindriopuntia imbricata} (tree cholla) and its ant mutualists. 
Tree cholla have a range which extends across the Southwest United States into Northern Mexico, with our study area set in New Mexico, US at the Sevilleta LTER.
These cacti flower in the spring throughout the summer, their reproductive season, outside of which they are not tended by ants. 
During the reproductive season these plants experience increased visitation by seed predators and herbivores, which influence their reproductive outputs, survival, growth, etc.
There are a number of observed ant partners which interact with the cacti in this part of their range, including \textit{Crematogaster opuntiae} (\textit{Crem.}), \textit{Liometopum apiculatum} (\textit{Liom.}), \textit{Forelius pruinosus}, an unidentified \textit{Camponotus} species, an unidentified \textit{Phenogaster} species, among others. 
The ants which most commonly interact with the cacti are \textit{Liom.} and \textit{Crem.}, while others are seen with low enough frequency that for the purpose of this paper we refer to them as ``other" ants. 
These ant partners are all in the same guild, meaning they all provide denfense to the cacti from insect herbivores and seed predators in return for extrafloral nectar (EFN).
The cacti in this mutualism are each tended by one species at a time, for their entire reproductive season with little turnover until the winter between reproductive seasons. 
Some of the ant partners are more effective defenders than others, with \textit{Liom.} tended reproducing plants experiencing the lowest level of herbivory as shown in Figure \ref{fig:herb}.
This shows that although all the ants associated with the tree cholla are within one guild, they are not all equal and may have different demographic effects on the cacti.

In this paper we will answer a number of questions about the demographic effects of partner diversity in multi-species mutualisms:
\begin{enumerate}
  \item{What are the contrasting demographic effects of multiple partners?}
  \item{What combination of ant partners is associated with the highest fitness for the tree cholla?}
  item{What mechanisms explain the effects of multiple ant partners on the tree cholla?}
\end{enumerate}

To answer these questions we used a long-term dataset of demographic information (size, survival, number of flowers produced or aborted, etc.) and ant partner data (species, number of ants) to track the structure of the population across time as well as individual level impacts of ant partners on the cacti. 
We analyzed the impacts of partner diversity on each individual vital rate (survivial, growth, floral-viability, etc.) with bayesian models, which we used to parameterize an Integral Projection Model (IPM).
With the IPM we moved beyond what has been done in previous studies\cite{Palmer2010} to identify which mechanisms explain the effects of partner diversity on the tree cholla.

We hypothesized that the cacti would experience the highest fitness when interacting with all partners observed in the field, meaning the current mutualism results in the highest fitness for the cacti.
We also hypothesized that complementarity would explain these positive effects of partner diversity in the multi-species mutualism.
\section*{Methods}
\subsection*{Study System}

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{amsfonts,amssymb,amsmath,amsthm}
\usepackage{multirow}
\usepackage{multicol}
\setlength{\columnsep}{1.5cm}
\usepackage{setspace}
\usepackage{url}
\usepackage{array}
\usepackage{xfrac}
\usepackage{mwe}
\usepackage{tikz}
\usepackage{lmodern}
\usepackage{flowchart}
\usetikzlibrary{shapes,arrows,positioning,calc,fit}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{booktabs}
\usepackage{float}
\usepackage{color,soul}
%\usepackage[numbers,sort&compress]{natbib}
\usepackage{hyperref}
%\usepackage{cite}
\usepackage{biblatex}
\addbibresource{References.bib}
\newcommand{\tom}[2]{{\color{red}{#1}}\footnote{\textit{\color{red}{#2}}}}
\newcommand{\ali}[2]{{\color{blue}{#1}}\footnote{\textit{\color{blue}{#2}}}}

@@

\section*{Introduction}
%BASELINE OF MUTUALISMS
Mutualisms are pairwise species interactions in which both participants benefit. 
They are among the most widespread species interactions\cite{Chamberlain2014,Stachowicz2005,BoucherDouglasH.1985} \tom{with diverse and dynamic consequences}{This sounds nice but does not carry much information. Consequences for what? And in what way are they diverse and dynamic?}. 
%\ali{The benefits from these interactions are called rewards, but they require investment of resources into the interaction}{I'm honestly not sure if I need to explain this idea? Do I need to include more basic mutualism background? I have tried to shift this so that I cover a small amount and then jump into the idea of partner diversity in mutualisms instead}. %no, I don't think you need this
\tom{Historically, scientists focused on pairwise mutualisms\cite{Bascompote2019}, however, in recent years multi-species mutualisms have been more heavily studied. }{It is not clear from this sentence whether you are implying that some mutualisms are pairwise and some are multi-species, or whether this distinction is just a matter of perspective. Either way, this is a sentence about how mutualisms are studied and not about mutualisms per se.}
While mutualism is defined at the level of a species pair (+/+) these interactions are embedded in multi-species communities, such that a focal species may engage with multiple partner species.
\tom{It has become apparent that partner diversity in mutualisms}{General comment in the spirit of constructive criticism: the ratio of words to information in your writing is high. Imagine this sentence started ``Partner diversity in mutualisms often leads...''. This has the same meaning, is more efficient, and sounds more declarative and authoritative.} often leads to non-additive fitness benefits for the focal mutualist\cite{Afkhami2014, Palmer2010}. 
\tom{This means benefits to a focal mutualist can be greater than, less than, or equal to the sum of the benefits observed in each of the  pairwise interactions that makes up the multi-species mutualism.}{This is correct, and interesting, but just noticing that you are priming the read for an analysis that you do not currently do (though you could and we could thinking about how).}
\tom{This is true for many complicated reasons}{Not a very scientific thing to say}, including \tom{interactions between the various partners, niche overlap, temporal resource variation, and differences in partner quality, functional benefit, and competitive ability}{I think this list requires more explanation to be informative, but this is probably not the place for it.}\cite{stanton2013, Afkhami2014,Boucher1982}.
Often partners have similar resource needs, particularly if they are in the same guild, which can lead to resource competition and \tom{fighting}{You are probably thinking about ants here. At this point in the paper you should be writing more generally.}, potentially reducing benefits, or to increased quality and frequency of benefits\cite{Bascompote2019,Stanton2003}.
For this reason, pairwise studies cannot be accurately used to predict the outcomes of multi-species mutualisms\cite{Palmer2010, Stanton2013. Chamberlain2014, Song2020} \tom{which are more common}{This relates to my comment above about how it's not clear whether you are describing mutualisms as intrinsically pairwise or multi-species, or whether this is about research approached. I don't think you have a solid foundation for saying that multi-species is more common.}.
\ali{***** Biodiversity ecosystem function? -- TOM: I would save this for next paragraph.}{After this I feel like I go straight into the mechanisms which explain the potential positive effects of diversity, but I don't specify that I am talking about those and I also don't talk about any explainations of negative effects? Maybe if I include the connection between BEF theory and mutualisms here it will make a nice bridge to the benefits of diversity?} 
\tom{Observational studies on the effects of diverse multi-species mutualism systems are necessary to help us understand the demographic effects of partner diversity in mutualisms. }{Good closing sentence but I would probably not emphasize observational.}

The diversity of partners in a multi-species mutualism causes varied demographic effects on the population of \tom{the focal mutualist}{I think you should introduce the idea of a `focal mutualist' more clearly.} which can be explained by a number of mechanisms.
Partners can vary in many ways: in some cases, the quality varies leading to some true mutualist partners, some freeloaders, and even some parasites\cite{Bronstein1994, Afkhami2014,Song2020,West2007,Frederickson2013}; in other cases, the functions of beneficial partners can vary, each offering a different type of reward to the focal mutualist \cite{Stanton2003}.
\tom{Partner quality variations can remain consistent across years and life stages of the focal mutualist or they can shift year to year or in response to different types of stressors. }{SHould cite.}
When partner quality remains consistent across time, meaning one partner is always better or worse than another, benefits of partner diversity may reflect a sampling effect, where a more diverse sample of the partner community may be more likely to include the ``best" one\cite{Batstone2018}.
When a focal mutualist in a multi-species mutualism \ali{experiences}{not sure if this is the right word - not the right word. A focal mutualist does not experience a sampling effect. The sampling effect is a mechanism for positive effects of diversity.} sampling effect the fitness of that focal mutualist should be equal to the fitness of the focal mutualist if they interacted only with the ``best" partner. 
In some cases the quality of partners is not constant, rather it varies year to year due to environmental limitations, \tom{such as resource shortages and niche shifts}{Unclear what this means.}.
The effects of partner diversity in these systems can be explained by the \tom{portfolio effect}{I would discuss this last, after sampling effect and complementarity.}, the idea that each partner is the \tom{``best"}{I would not keep using this in quotations and instead find the right scientific language for what you are trying to say.} under a different set of conditions, which vary temporally\cite{Winfree2020,Batstone2018}. 
This mechanism works almost like a financial portfolio, when one partner has a bad year another partner has a good year, meaning the overall fitness benefits of the interactions remain relatively constant across temporal variation\cite{Batstone2018}.
Finally, partners can vary functionally, meaning each partner offers a different type of reward to the focal mutualist. 
The effects of partner functional diversity can be explained by complementarity, the idea that each partner may account for some part of the benefits, but each has different functional pathways, which together can aid in broader benefits\cite{Winfree2020,Batstone2018}.
\tom{This variation can be both within and outside of a guild, meaning the variation can be very large, such as the difference between pollination and defense among other functions\cite{Bronstein2006}, or relatively small, such as similar rewards across different life stages\cite{Stanton2003}. }{I got stuck on this sentence and I am unsure what you are trying to communicate.}
Complementarity in a system is evidenced by synergistic benefits, meaning the fitness of the focal mutualist is higher than the fitness if the focal mutualist interacted with any one ``best" partner\cite{Batstone2018}. 
\ali{These three mechanism could explain the positive partner diversity effects on a focal mutualist in a multi-species mutualism, if these benefits exist.}{I am struggling on the transition between this paragraph and the next. Tom: there is no new information in this sentence, so I don't think you need it.}

\tom{For reasons I mentioned, you need to provide conceptual context and background information on partner turnover, probably as a new paragraph here (or elsewhere in the Intro).}{}

\tom{Multi-species mutualisms are a huge group of interactions which vary considerably.}{There is no information in this sentence.}
\tom{While there are many types of mutualistic interactions, including pollination, defense, dispersal, housing, and many more\cite{Bronstein2006} in this paper we will focus on defensive ant-plant mutualisms.}{Not an effective sentence. Don't list the things the paper is not about. Instead, explain why ant-plant systems are a relevant and valuable context for studying effects of partner diversity.}
These involve plants which provide extra-floral nectar and/or ``housing'' to ants which in turn defend them from herbivores\cite{Bronstein1998}. 
While these interactions have been well studied\cite{} in the literature, \tom{few have considered how diversity within ant defender guilds affect the overall benefits of mutualism for the plant partner. }{Cite. Also worth pointing out that I don't think any previous study has incorporated temporal fluctuations, i.e. portfolio effect.}

This study focuses on the long lived \textit{Cylindriopuntia imbricata} (tree cholla) and its ant mutualists. 
\tom{Tree cholla have a range which extends across the Southwest United States into Northern Mexico, with our study area set in New Mexico, US at the Sevilleta LTER.}{Like much of this paragraph, this information is more appropriate for the Study System section of the methods. I am not flagging all of that here, but note that much of this paragraph should change.}
These cacti flower in the spring throughout the summer, their reproductive season, outside of which they are not tended by ants. 
During the reproductive season these plants experience increased visitation by seed predators and herbivores, which influence their reproductive outputs, survival, growth, etc.
There are a number of observed ant partners which interact with the cacti in this part of their range, including \textit{Crematogaster opuntiae} (\textit{Crem.}), \textit{Liometopum apiculatum} (\textit{Liom.}), \textit{Forelius pruinosus}, an unidentified \textit{Camponotus} species, an unidentified \textit{Phenogaster} species, among others. 
The ants which most commonly interact with the cacti are \textit{Liom.} and \textit{Crem.}, while others are seen with low enough frequency that for the purpose of this paper we refer to them as ``other" ants. 
These ant partners are all in the same guild, meaning they all provide denfense to the cacti from insect herbivores and seed predators in return for extrafloral nectar (EFN).
The cacti in this mutualism are each tended by one species at a time, for their entire reproductive season with little turnover until the winter between reproductive seasons. 
Some of the ant partners are more effective defenders than others, with \textit{Liom.} tended reproducing plants experiencing the lowest level of herbivory as shown in Figure \ref{fig:herb}.
This shows that although all the ants associated with the tree cholla are within one guild, they are not all equal and may have different demographic effects on the cacti.\tom{}{This paragraph is a little chaotic. There is natural history info, methods, and results! Needs to be tightened up. What do you notice in other papers that you read about how study systems are first described? This should help guide your writing.}

In this paper we will answer \tom{a number}{WHat is the number?} of questions about the demographic effects of partner diversity in multi-species mutualisms:
\begin{enumerate}
  \item{What are the contrasting demographic effects of multiple partners?}
  \item{What combination of ant partners is associated with the highest fitness for the tree cholla?}
  item{What mechanisms explain the effects of multiple ant partners on the tree cholla?}
\end{enumerate}

To answer these \tom{questions}{I think the questions can be refined further, plus we need the turnover question in there.} we used a long-term dataset of demographic information (size, survival, number of flowers produced or aborted, etc.) and ant partner data (species, number of ants) to track the structure of the population across time as well as individual level impacts of ant partners on the cacti. 
We analyzed the impacts of partner diversity on each individual vital rate (survivial, growth, floral-viability, etc.) with Bayesian statistical models, which we used to parameterize an Integral Projection Model (IPM).
With the IPM we moved \tom{beyond what has been done in previous studies\cite{Palmer2010}}{If you are going to say this it's important to describe what has been done and how this study goes beyond it.} to identify which mechanisms explain the effects of partner diversity on the tree cholla. \tom{}{Generally this paragraph is a good, quick overview of what we did - good way to wrap up the Intro.}

tom{We hypothesized that the cacti would experience the highest fitness when interacting with all partners observed in the field, meaning the current mutualism results in the highest fitness for the cacti.
We also hypothesized that complementarity would explain these positive effects of partner diversity in the multi-species mutualism.}{This is a stylistic thing but I don't think that explicit hypotheses are necessary as long as there are clear and compelling questions.}

\section*{Methods}
\subsection*{Study System}
